CloneOverflow: \\ Discovery of Online Code Clones between \\Stackoverflow and Open Source Projects

### 2016-10-20 latex-acm/cloneoverflow.tex
Updated latex

\documentclass{sig-alternate-05-2015}
\usepackage{graphicx}
\usepackage{graphics}
\usepackage{listings}  
\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\usepackage{multirow}
\usepackage[table]{xcolor}
\usepackage{float}
\usepackage{array}
\usepackage{ragged2e}
\newcolumntype{P}[1]{>{\RaggedRight\hspace{0pt}}p{#1}}

@@

\title{Clone Overflow: \\ Code Reuse in Online Corpora and Its Effects}

\numberofauthors{1}
\author{
	\alignauthor
	Chaiyong Ragkhitwetsagul, Jens Krinke \\
	\affaddr{University College London}\\
	\affaddr{London, UK}
}

@@

\section{Introduction}

\section{Research Questions}
\textbf{RQ1 (online code clone):} \textit{How source code are reused between between Q\&A sites and open source projects?} We would like to observe whether this phenomenon has happened and at what scale. \newline
\textbf{RQ2 (flow of online code clone):} \textit{what are the directions source code have been reused?} If the code reuse between the two locations exist, we would like to discover the which direction the code that have been copied. Is it from Q\&A site to open source projects, or the other way around, or both? \newline
\textbf{RQ3 (classification of online code clone):} \textit{How and why did these online code clone happen?} Can we categorise them? \newline
\textbf{RQ4 (effects of online code clone):} \textit{ Is this phenomenon of online code clone harmful and how?} is there any evidence of problems caused by reusing code between Q\&A sites and open source projects?

@@

\subsection{Dataset}
In our study, we selected Qualitas corpus containing 64 Java open source projects \cite{QualitasCorpus}. However, we found that \textit{eclipse} project does not contain source code so we removed it from the dataset. This results in totally 63 projects being analysed. The details of the 63 Qualitas projects are listed in Table \ref{t:new_and_old}.

\subsection{Code Similarity Measurement}
We selected two clone detectors for this study: Simian \cite{simian} and NiCad \cite{Cordy,Roy2008}. \FIXME{Add more info about clone detection tools in general and more details of these two tools}

@@

\begin{table*}[h]
	\centering
	\caption{Qualitas-\textit{O} (2013-09-01r) clone results}
	\label{t_simian_raw_results}
%	\resizebox{\columnwidth}{!}{%
	\small
		\begin{tabular}{l|r|r|r|r|r|r|r|r|r|r|r|r}
			\hline
			\multirow{3}{*}{Statistics} 
			& \multicolumn{3}{c|}{Simian Default settings} 
			& \multicolumn{3}{c|}{Simian FSE'13 settings}
			& \multicolumn{3}{c|}{NiCad Default settings} 
			& \multicolumn{3}{c}{NiCad FSE'13 settings} \\ \cline{2-13} 
			& \multicolumn{3}{c|}{792 fragments} 
			& \multicolumn{3}{c|}{1229 fragments}  
			& \multicolumn{3}{c|}{1141 fragments} 
			& \multicolumn{3}{c}{12400 fragments} \\ \cline{2-13}
			%& \multicolumn{3}{c|}{iCharC,iCurlB,iIdC,iMod,iStrC} 
			%& \multicolumn{3}{c|}{iCurlB,iId,iIdC,iStr,iChar,iSbtNm,bSqBrck} 
			%& \multicolumn{3}{c|}{rename=none,abstract=none} 
			%& \multicolumn{3}{c}{rename=blind,abstract=literal} \\ %\cline{2-17}  
			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$
			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\ 
			\hline
			%Removed & 11 & -- & -- & -- & 0 & -- & -- & -- & -- & -- & -- & -- & -- & -- & -- & -- \\ %& 11 & -- & -- & -- \\
			Total & 24,929 & -- & -- & 16,957,362 & --	& -- & 105,118 	& -- & -- & 113,557,298 & -- & -- \\
			Mean & 38 & 7.54 & 0.27 & 14,444 & 4.80 & 0.28 & 107 & 9.52 & 0.25 & 9,397 & 5.21 & 0.20 \\
			Std Dev. & 87 & 3.21 & 0.22 & 281,747 & 1.22 & 0.18 & 198 & 3.07 & 0.18 & 12,098 & 1.73 & 0.16 \\
			Max  & 551 & 49.00 & 0.94 & 9,599,676 & 18.00 & 0.89 & 1,792 & 39.00 & 0.80 & 227,077 & 44.00 & 0.86 \\
			Min  & 1 & 5.00 & 0.01 & 1 & 4.00 & 0.02 & 1 & 7.00 & 0.02 & 1 & 3.00 & 0.01 \\
			Median  & 3 & 7.00 & 0.23 & 22 & 5.00 & 0.24 & 15 & 8.00 & 0.19 & 6,105 & 5.00 	& 0.15 \\
			Mode  & 1 & 7.00 & 0.25 & 1 & 4.00 & 0.50 & 1 & 8.00 & 0.53 & 1 & 4.00 & 0.33 \\
			\hline
		\end{tabular} %
%	}
\end{table*}

\begin{table*}
	\centering
	\caption{Qualitas-\textit{N} (2016-08-05) clone results (44 new Qualitas projects)}
	\label{t_simian_raw_results}
%	\resizebox{\columnwidth}{!}{%
	\small
		\begin{tabular}{l|r|r|r|r|r|r|r|r|r|r|r|r}
			\hline
			\multirow{3}{*}{Statistics} 
			& \multicolumn{3}{c|}{Simian Default settings} 
			& \multicolumn{3}{c|}{Simian FSE'13 settings} 
			& \multicolumn{3}{c|}{NiCad Default settings} 
			& \multicolumn{3}{c}{NiCad FSE'13 settings} \\ \cline{2-13} 
			& \multicolumn{3}{c|}{707 fragments} 
			& \multicolumn{3}{c|}{1205 fragments} 
			& \multicolumn{3}{c|}{1068 fragments} 
			& \multicolumn{3}{c}{10231 fragments} \\  \cline{2-13}
			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$
			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\
			\hline
			Total & 60,536 & -- 	& -- 	& 22,797,190 & -- 	& --  & 648,165 & -- & -- & 573,438,528 & -- & -- \\ 
			Mean 	& 86 	& 7.37 	& 0.26 	& 18,919 	& 4.85 	& 0.28 & 607 & 9.39 & 0.25 & 47663 & 5.22 & 0.20 \\
			Std Dev. & 217 	& 2.22 	& 0.21 	& 326,588 	& 1.31 	& 0.19 & 1,499 & 2.98 & 1.81 & 58,833 & 2.77 & 0.15 \\
			Max 	& 1,298 & 32.00 & 0.94 & 11,127,286 & 21.00 & 0.92 & 10,550 & 36.00 & 0.84 & 1,246,598 & 250 & 0.96 \\
			Min 	& 1 	& 5.00 	& 0.01 	& 1 & 4.00 	& 0.02 & 1 & 7 & 0.02 & 1 & 2.00 & 0.01\\
			Median 	& 2 & 7.00 	& 0.21 	& 20		& 5.00 	& 0.25 & 33 & 8 & 0.19 & 52,077 & 5.00 & 0.15 \\
			Mode & 1 	& 7.00 	& 0.25 	& 1 		& 4.00 	& 0.50 & 1 & 8 & 0.67 & 1 & 4.00 & 0.33 \\
			\hline
		\end{tabular} %
	%}
\end{table*}

@@

	\caption{63 Qualitas projects (new versions checked on 2016-09-27)}

@@

For agreement-based clone pairs, we use the threshold of 0.7 for both \textit{good}-match and \textit{ok}-match. Visualisation of \textit{good}-match common clone pairs between sets of parameter settings can be seen from Figure \ref{fig:venn4_orig_good}. There are 1,357 unique \textit{good}-match pairs. The \textit{ok}-match subsumes the \textit{good}-match resulting in totally 10,139 common clone pairs (Figure \ref{fig:venn4_orig_ok}).

However, for NiCad's settings, we found a few renaming and clustering errors which resulted in fewer projects with clone reports. For NiCad default settings (NiCad$_{\textrm{\textit{df}}}$), 6 projects had clustering failed errors. For NiCad FSE13 settings (NiCad$_{fse13}$), 4 projects had renaming failed errors and 13 projects had clustering failed errors as depicted in Table \ref{tab:projects_missing}. So these projects are also missing from agreed clone pairs. \FIXME{Report the errors to NiCad creator.}

@@

\begin{table*}
	\centering
	\caption{No.~of projects in Qualitas Original~(Qualitas-\textit{O}) and New (Qualitas-\textit{N}) successfully analysed by Simian and NiCad}
	\label{tab:projects_missing}
	\small
	\begin{tabular}{r|r|r|r|r|r}
		\hline
		\multicolumn{3}{c|}{Qualitas-\textit{O}} & \multicolumn{3}{c}{Qualitas-\textit{N}} \\
		\hline
		Simian$_{\textrm{\textit{df/fse13}}}$ & NiCad$_{\textrm{\textit{df}}}$ & NiCad$_{fse13}$ & Simian$_{\textrm{\textit{df/fse13}}}$ & NiCad$_{\textrm{\textit{df}}}$ & NiCad$_{fse13}$ \\ \hline
		63	& 57 & 46 & 44 & 40 & 34 \\
		\hline
		& \textit{6 clustering failed} & \textit{13 clustering failed} & & \textit{4 clustering failed} & \textit{6 clustering failed} \\
		& cayenne   & cayenne 	& & jboss (wildfly) & ArgoUML \\
		& checkstyle & checkstyle & & hadoop & checkstyle \\
		& db-derby 	& db-derby 	& & db-derby & db-derby \\
		& geotools 	& geotools  & & hibernate & cayenne \\
		& iReport 	& iReport   & & & jena \\
		& hibernate & ArgoUML 	& & & geotools \\
		&			& castor 		& & & \\
		&			& drjava 		& & & \\
		&			& ganttproject 	& & & \\
		&			& ivatagroupware & & &  \\
		&			& jasperreports & & & \\
		&			& jboss 		& & & \\
		&			& jchempaint 	& & & \\
		\hline
		& 			&  \textit{4 renaming failed} & & & \textit{4 renaming failed} \\
		&			& Vuze 		& & & Vuze \\
		&			& aspectj 	& & & hadoop \\
		&			& eXoPortal 	& & & jboss (wildfly) \\
		&			&  hibernate 	& & & hibernate \\
		\hline
	\end{tabular}
\end{table*}

\begin{table}
	\centering
	\caption{Distribution of agreement-based clone pairs reported using Bellon's criteria}
	\label{t_agreed_good_clone_pairs}
	\begin{tabular}{l|l|r|r}
		\hline
		\multicolumn{2}{c|}{Tool} & \multicolumn{2}{c}{Qualitas-\textit{O}} \\
		\hline
		Simian & NiCad & \textit{good}-match & \textit{ok}-match \\
		%\hline
		%Settings & Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{fse13}}}$ & Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{fse13}}}$ \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
		\hline
		\textit{default} & \textit{default} & 9 	& 473 \\ 
		\textit{default} & \textit{fse13} 	& 12 	& 353 \\ 
		\textit{fse13} 	& \textit{default} 	& 7 	& 60 \\
		\textit{fse13} 	& \textit{fse13} 	& 1,338 & 9528 \\ 
		\hline
		\multicolumn{2}{l|}{Total} & 1,366 & 10,414 \\
		\multicolumn{2}{l|}{Total (unique)} & 1,357 & 10,139 \\
		\hline
	\end{tabular}
\end{table}

\begin{figure*}
	\centering
	\begin{minipage}{.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{venn4_pairs_good}
		\caption{Qualitas-\textit{O} \textit{good}-match(0.7) pairs}
		\label{fig:venn4_orig_good}
	\end{minipage}%
	\begin{minipage}{.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{venn4_pairs_ok}
		\caption{Qualitas-\textit{O} \textit{ok}-match(0.7) pairs}
		\label{fig:venn4_orig_ok}
	\end{minipage}
\end{figure*}

@@

The classification scheme is described in Table \ref{tab:classification_scheme} and the classification results are shown in Table \ref{tab:classification_good_o}. We have manually investigated all of the 1,357 \textit{good-match} ones reported by agreement of four different Simian and NiCad settings.  However, for the \textit{ok-match}, we could not investigate all of the 10,139 pairs manually.  According to the distribution of category from \textit{good-match} results, we can see that Simian$_{fse13}$--NiCad$_{fse13}$ produces a large number, 1,338, of false positive results (D, E, and F). Thus, we decided to leave them out of the manual investigation of \textit{ok-match} pairs. There are totally 608 \textit{ok-match} pairs that were investigated. The 39 true positive pairs found are combinations of 8 unique Stackoverflow fragments, and 9 unique Qualitas Java files from 6 different projects.

@@

%\textbf{Qualitas-\textbf{N}:} We decided to filter out the agreed clone pairs reported by agreement of Simian$_{\mathrm{\textit{fse13}}}$-NiCad$_{\mathrm{\textit{fse13}}}$ altogether due to its large number of false positive. With the remaining 3 agreements, we did manual investigation of agreed \textit{ok}-match clone pairs from agreements of Simian$_{df}$-NiCad$_{df}$, Simian$_{df}$-NiCad$_{\mathrm{\textit{fse13}}}$, and Simian$_{\mathrm{\textit{fse13}}}$-NiCad$_{df}$. We had not done any investigation of \textit{good}-match since there were no \textit{good}-match pairs for these 3 agreements. The number of pairs that have been looked at is 6,706 (excluding duplicates). The results are shown in Table.

\begin{table*}
	\centering
	\caption{Qualitas-\textit{O}: Classification results of \textit{good-} and \textit{ok}-match pairs which excludes the subsumed \textit{good}-match and Simian$_{\mathrm{\textit{fse13}}}$-NiCad$_{\mathrm{\textit{fse13}}}$ pairs.}
	\label{tab:classification_good_o}
	\small
	\begin{tabular}{|l"r|r|r|r|r|r|r|r"r|r|r|r|r|r|r"r|r|r|r|}
		\hline
		Classificaiton & A & A' & B & C & \textbf{Sum} & S$_{u}$ & Q$_u$ & Q$_{up}$ & D  & E & F & \textbf{Sum} & S$_{u}$ & Q$_u$ & Q$_{up}$ & \textbf{Total}  & S$_{u}$ & Q$_u$ & Q$_{up}$\\ 
		\hline 
		\multirow{1}{*}{\textit{good-match(0.7)}}  & 1 & 0 & 1  & 3 & \textbf{5} & 5 & 4 & 4 & 26  & 6 & 1320 & \textbf{1352} & 56 & 402 & 31 & \textbf{1357} & 61 & 406 & 32 \\
		\multirow{1}{*}{\textit{ok-match(0.7)}}  & 8 & 0 & 23  & 8 & \textbf{39} & 8 & 9 & 6 & 480 & 28 & 61 & \textbf{569} & 76 & 60 & 16 & \textbf{608} & 83 & 68 & 19 \\
		\hline
	\end{tabular} 
\end{table*}

@@

With our 4 settings, we decided to investigate only 2 settings, Simian$_{df}$, and NiCad$_{df}$, and drop Simian$_{\mathrm{\textit{fse13}}}$ and NiCad$_{\mathrm{\textit{fse13}}}$ due to their large number of false positives as shown in Table \ref{tab:good_classification} and \ref{tab:ok_classification}. With the 2 selected settings, we investigated clone pairs having the minimum clone size of 10 SLOC as they are meaningful and tend to be real clone in modern clone detection \cite{Sajnani2016}.

@@

\subsection{Issue~1:~outdated online code}
After located and classified all the online clone pairs, we are now interested in analysing the true online clone pairs that are copied in the direction of Q $\rightarrow$ S (class-\textit{A} online clone pairs) in Table \ref{tab:classification_true_pairs_summary} which results in 48 pairs selected. We restricted it further to only the ones having versioning system so we can trace changes made to these clone pairs. Fortunately, all of the pairs were from projects with either git or svn so we did not remove any pair from this set.

>>>>

\documentclass{sig-alternate-05-2015}
\usepackage[utf8]{inputenc}
\usepackage[italian]{babel}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{graphics}
\usepackage{listings}  
\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\usepackage{multirow}
\usepackage[table]{xcolor}
\usepackage{float}
\usepackage{array}
\usepackage{ragged2e}
\newcolumntype{P}[1]{>{\RaggedRight\hspace{0pt}}p{#1}}

@@

\title{CloneOverflow: \\ Discovery of Online Code Clones between \\Stackoverflow and Open Source Projects}

\numberofauthors{1}
\author{
	\alignauthor
	$^1$Chaiyong Ragkhitwetsagul, $^1$Jens Krinke, $^2$Giuseppe Bianco \\
	\affaddr{$^1$University College London, London, UK}\\
	\affaddr{$^2$Università degli Studi del Molise, Campobasso, Italy}
}

@@

\section{Introduction}
\begin{itemize}
	\item Definition of code clones, online code clones, pros \& cons
	\item Roles of Q\&A websites in supporting software development and education
	\item Problems of code reuse (bug propagation, licensing conflicts)
\end{itemize}

This paper makes the following  primary contributions:

\vspace{0.5ex}%
\noindent\textbf{1.~A manual study of online code clone between Stackoverflow and open source projects:} 
We manually investigate 2,371 clone pairs found between Java code fragments obtained from Stackoverflow accepted answers, and 63 Java open source projects.

\vspace{0.5ex}%
\noindent\textbf{2.~Addressing the problems of reusing online code clones:} Our study shows that there are at least 48 clones that have been copied from open source projects to Stackoverflow as code examples which may violate their software license. Moreover, out of 48 clones, there are 27 clones in Stackoverflow that are outdated and dangerous for being reused.

\section{Research Questions}
The study aims to answer the following research questions: \\ 
\textbf{RQ1 (online code clone):} \textit{How source code are reused between between Q\&A sites and open source projects?} We would like to observe whether this phenomenon has happened and at what scale. \newline
\textbf{RQ2 (flow of online code clone):} \textit{what are the directions source code have been reused?} If the code reuse between the two locations exist, we would like to discover the which direction the code that have been copied. Is it from Q\&A site to open source projects, or the other way around, or both? \newline
\textbf{RQ3 (classification of online code clone):} \textit{How and why did these online code clone happen?} Can we categorise them? \newline
\textbf{RQ4 (effects of online code clone):} \textit{ Is this phenomenon of online code clone harmful and how?} is there any evidence of problems caused by reusing code between Q\&A sites and open source projects?

@@

\subsection{Dataset}
In our study, we selected Qualitas corpus containing 64 Java open source projects \cite{QualitasCorpus}. We found that \textit{eclipse} project does not contain source code so we removed it from the dataset. This results in totally 63 projects being analysed. The details of the 63 Qualitas projects with their respective licenses are listed in Table \ref{t:new_and_old}.

\subsection{Clone Detectors}
We selected two clone detectors for this study: Simian \cite{simian} and NiCad \cite{Cordy,Roy2008}. \FIXME{Add more info about clone detection tools in general and more details of these two tools}

\subsection{Agreement-based Clone Detection}
We adopted an idea of clone agreement normally used in clone research \cite{Wang2013,Funaro2010}.

@@

\begin{table*}[h]
	\centering
	\caption{Qualitas-\textit{O} (2013-09-01r) clone results}
	\label{t_simian_raw_results}
%	\resizebox{\columnwidth}{!}{%
	\small
		\begin{tabular}{l|r|r|r|r|r|r|r|r|r|r|r|r}
			\hline
			\multirow{3}{*}{Statistics} 
			& \multicolumn{3}{c|}{Simian Default settings} 
			& \multicolumn{3}{c|}{Simian EvaClone settings}
			& \multicolumn{3}{c|}{NiCad Default settings} 
			& \multicolumn{3}{c}{NiCad EvaClone settings} \\ \cline{2-13} 
			& \multicolumn{3}{c|}{792 fragments} 
			& \multicolumn{3}{c|}{1229 fragments}  
			& \multicolumn{3}{c|}{1141 fragments} 
			& \multicolumn{3}{c}{12400 fragments} \\ \cline{2-13}
			%& \multicolumn{3}{c|}{iCharC,iCurlB,iIdC,iMod,iStrC} 
			%& \multicolumn{3}{c|}{iCurlB,iId,iIdC,iStr,iChar,iSbtNm,bSqBrck} 
			%& \multicolumn{3}{c|}{rename=none,abstract=none} 
			%& \multicolumn{3}{c}{rename=blind,abstract=literal} \\ %\cline{2-17}  
			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$
			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\ 
			\hline
			%Removed & 11 & -- & -- & -- & 0 & -- & -- & -- & -- & -- & -- & -- & -- & -- & -- & -- \\ %& 11 & -- & -- & -- \\
			Total & 24,929 & -- & -- & 16,957,362 & --	& -- & 105,118 	& -- & -- & 113,557,298 & -- & -- \\
			Mean & 38 & 7.54 & 0.27 & 14,444 & 4.80 & 0.28 & 107 & 9.52 & 0.25 & 9,397 & 5.21 & 0.20 \\
			Std Dev. & 87 & 3.21 & 0.22 & 281,747 & 1.22 & 0.18 & 198 & 3.07 & 0.18 & 12,098 & 1.73 & 0.16 \\
			Max  & 551 & 49.00 & 0.94 & 9,599,676 & 18.00 & 0.89 & 1,792 & 39.00 & 0.80 & 227,077 & 44.00 & 0.86 \\
			Min  & 1 & 5.00 & 0.01 & 1 & 4.00 & 0.02 & 1 & 7.00 & 0.02 & 1 & 3.00 & 0.01 \\
			Median  & 3 & 7.00 & 0.23 & 22 & 5.00 & 0.24 & 15 & 8.00 & 0.19 & 6,105 & 5.00 	& 0.15 \\
			Mode  & 1 & 7.00 & 0.25 & 1 & 4.00 & 0.50 & 1 & 8.00 & 0.53 & 1 & 4.00 & 0.33 \\
			\hline
		\end{tabular} %
%	}
\end{table*}

\begin{table*}
	\centering
	\caption{Qualitas-\textit{N} (2016-08-05) clone results (44 new Qualitas projects)}
	\label{t_simian_raw_results}
%	\resizebox{\columnwidth}{!}{%
	\small
		\begin{tabular}{l|r|r|r|r|r|r|r|r|r|r|r|r}
			\hline
			\multirow{3}{*}{Statistics} 
			& \multicolumn{3}{c|}{Simian Default settings} 
			& \multicolumn{3}{c|}{Simian EvaClone settings} 
			& \multicolumn{3}{c|}{NiCad Default settings} 
			& \multicolumn{3}{c}{NiCad EvaClone settings} \\ \cline{2-13} 
			& \multicolumn{3}{c|}{707 fragments} 
			& \multicolumn{3}{c|}{1205 fragments} 
			& \multicolumn{3}{c|}{1068 fragments} 
			& \multicolumn{3}{c}{10231 fragments} \\  \cline{2-13}
			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$
			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\
			\hline
			Total & 60,536 & -- 	& -- 	& 22,797,190 & -- 	& --  & 648,165 & -- & -- & 573,438,528 & -- & -- \\ 
			Mean 	& 86 	& 7.37 	& 0.26 	& 18,919 	& 4.85 	& 0.28 & 607 & 9.39 & 0.25 & 47663 & 5.22 & 0.20 \\
			Std Dev. & 217 	& 2.22 	& 0.21 	& 326,588 	& 1.31 	& 0.19 & 1,499 & 2.98 & 1.81 & 58,833 & 2.77 & 0.15 \\
			Max 	& 1,298 & 32.00 & 0.94 & 11,127,286 & 21.00 & 0.92 & 10,550 & 36.00 & 0.84 & 1,246,598 & 250 & 0.96 \\
			Min 	& 1 	& 5.00 	& 0.01 	& 1 & 4.00 	& 0.02 & 1 & 7 & 0.02 & 1 & 2.00 & 0.01\\
			Median 	& 2 & 7.00 	& 0.21 	& 20		& 5.00 	& 0.25 & 33 & 8 & 0.19 & 52,077 & 5.00 & 0.15 \\
			Mode & 1 	& 7.00 	& 0.25 	& 1 		& 4.00 	& 0.50 & 1 & 8 & 0.67 & 1 & 4.00 & 0.33 \\
			\hline
		\end{tabular} %
	%}
\end{table*}

@@

	\caption{63 Qualitas projects (new versions retrieved on 2016-09-27)}

@@

For agreement-based clone pairs, we use a threshold of 0.7 for both \textit{good} and \textit{ok}-match. A visualisation of \textit{good}-match common clone pairs between four sets of parameter settings can be seen from Figure \ref{fig:venn4_orig_good}. There are 1,357 unique \textit{good}-match pairs. The distribution of 10,139 \textit{ok}-match pairs, which subsume the \textit{good}-match pairs, is depicted in Figure \ref{fig:venn4_orig_ok}.

Nevertheless,  NiCad produced renaming and clustering errors for some of the settings. This resulted in not all 63 projects had NiCad clone reports. For NiCad default settings (NiCad$_{\textrm{\textit{df}}}$), 6 projects had clustering failed errors. For NiCad EvaClone settings (NiCad$_{\textrm{\textit{EvaClone}}}$), 4 projects had renaming failed errors and 13 projects had clustering failed errors as depicted in Table \ref{tab:projects_missing}. So these projects are also missing from agreed clone pairs. \FIXME{Report the errors to NiCad creator.}

@@

\begin{table*}
	\centering
	\caption{No.~of projects in Qualitas Original~(Qualitas-\textit{O}) and New (Qualitas-\textit{N}) successfully analysed by Simian and NiCad}
	\label{tab:projects_missing}
	\small
	\begin{tabular}{r|r|r|r|r|r}
		\hline
		\multicolumn{3}{c|}{Qualitas-\textit{O}} & \multicolumn{3}{c}{Qualitas-\textit{N}} \\
		\hline
		Simian$_{\textrm{\textit{df/EvaClone}}}$ & NiCad$_{\textrm{\textit{df}}}$ & NiCad$_{\textrm{\textit{EvaClone}}}$ & Simian$_{\textrm{\textit{df/EvaClone}}}$ & NiCad$_{\textrm{\textit{df}}}$ & NiCad$_{\textrm{\textit{EvaClone}}}$ \\ \hline
		63	& 57 & 46 & 44 & 40 & 34 \\
		\hline
		& \textit{6 clustering failed} & \textit{13 clustering failed} & & \textit{4 clustering failed} & \textit{6 clustering failed} \\
		& cayenne   & cayenne 	& & jboss (wildfly) & ArgoUML \\
		& checkstyle & checkstyle & & hadoop & checkstyle \\
		& db-derby 	& db-derby 	& & db-derby & db-derby \\
		& geotools 	& geotools  & & hibernate & cayenne \\
		& iReport 	& iReport   & & & jena \\
		& hibernate & ArgoUML 	& & & geotools \\
		&			& castor 		& & & \\
		&			& drjava 		& & & \\
		&			& ganttproject 	& & & \\
		&			& ivatagroupware & & &  \\
		&			& jasperreports & & & \\
		&			& jboss 		& & & \\
		&			& jchempaint 	& & & \\
		\hline
		& 			&  \textit{4 renaming failed} & & & \textit{4 renaming failed} \\
		&			& Vuze 		& & & Vuze \\
		&			& aspectj 	& & & hadoop \\
		&			& eXoPortal 	& & & jboss (wildfly) \\
		&			&  hibernate 	& & & hibernate \\
		\hline
	\end{tabular}
\end{table*}

\begin{table}
	\centering
	\caption{Distribution of agreement-based clone pairs reported using Bellon's criteria}
	\label{t_agreed_good_clone_pairs}
	\begin{tabular}{l|l|r|r}
		\hline
		\multicolumn{2}{c|}{Tool} & \multicolumn{2}{c}{Qualitas-\textit{O}} \\
		\hline
		Simian & NiCad & \textit{good}-match & \textit{ok}-match \\
		%\hline
		%Settings & Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{EvaClone}}}$ & Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{EvaClone}}}$ \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
		\hline
		\textit{default} & \textit{default} & 9 	& 473 \\ 
		\textit{default} & \textit{EvaClone} 	& 12 	& 353 \\ 
		\textit{EvaClone} 	& \textit{default} 	& 7 	& 60 \\
		\textit{EvaClone} 	& \textit{EvaClone} 	& 1,338 & 9528 \\ 
		\hline
		\multicolumn{2}{l|}{Total} & 1,366 & 10,414 \\
		\multicolumn{2}{l|}{Total (unique)} & 1,357 & 10,139 \\
		\hline
	\end{tabular}
\end{table}

\begin{figure*}
	\centering
	\begin{minipage}{.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{venn4_pairs_good}
		\caption{\textit{good}-match(0.7) pairs}
		\label{fig:venn4_orig_good}
	\end{minipage}%
	\begin{minipage}{.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{venn4_pairs_ok}
		\caption{\textit{ok}-match(0.7) pairs}
		\label{fig:venn4_orig_ok}
	\end{minipage}
\end{figure*}

@@

The classification scheme is described in Table \ref{tab:classification_scheme} and the classification results are shown in Table \ref{tab:classification_good_o}. We have manually investigated all of the 1,357 \textit{good-match} ones reported by agreement of four different Simian and NiCad settings.  However, for the \textit{ok-match}, we could not investigate all of the 10,139 pairs manually.  According to the distribution of category from \textit{good-match} results, we can see that Simian$_{\textrm{\textit{EvaClone}}}$--NiCad$_{\textrm{\textit{EvaClone}}}$ produces a large number, 1,338, of false positive results (D, E, and F). Thus, we decided to leave them out of the manual investigation of \textit{ok-match} pairs. There are totally 608 \textit{ok-match} pairs that were investigated. The 39 true positive pairs found are combinations of 8 unique Stackoverflow fragments, and 9 unique Qualitas Java files from 6 different projects.

@@

%\textbf{Qualitas-\textbf{N}:} We decided to filter out the agreed clone pairs reported by agreement of Simian$_{\mathrm{\textit{EvaClone}}}$-NiCad$_{\mathrm{\textit{EvaClone}}}$ altogether due to its large number of false positive. With the remaining 3 agreements, we did manual investigation of agreed \textit{ok}-match clone pairs from agreements of Simian$_{df}$-NiCad$_{df}$, Simian$_{df}$-NiCad$_{\mathrm{\textit{EvaClone}}}$, and Simian$_{\mathrm{\textit{EvaClone}}}$-NiCad$_{df}$. We had not done any investigation of \textit{good}-match since there were no \textit{good}-match pairs for these 3 agreements. The number of pairs that have been looked at is 6,706 (excluding duplicates). The results are shown in Table.

\begin{table*}
	\centering
	\caption{Qualitas-\textit{O}: Classification results of \textit{good-} and \textit{ok}-match pairs which excludes the subsumed \textit{good}-match and Simian$_{\mathrm{\textit{EvaClone}}}$-NiCad$_{\mathrm{\textit{EvaClone}}}$ pairs.}
	\label{tab:classification_good_o}
	\small
	\begin{tabular}{|l"r|r|r|r|r|r|r|r"r|r|r|r|r|r|r"r|r|r|r|}
		\hline
		Classificaiton & A & A' & B & C & \textbf{Sum} & S$_{u}$ & Q$_u$ & Q$_{up}$ & D  & E & F & \textbf{Sum} & S$_{u}$ & Q$_u$ & Q$_{up}$ & \textbf{Total}  & S$_{u}$ & Q$_u$ & Q$_{up}$\\ 
		\hline 
		\multirow{1}{*}{\textit{good-match(0.7)}}  & 1 & 0 & 1  & 3 & \textbf{5} & 5 & 4 & 4 & 26  & 6 & 1320 & \textbf{1352} & 56 & 402 & 31 & \textbf{1357} & 61 & 406 & 32 \\
		\multirow{1}{*}{\textit{ok-match(0.7)}}  & 8 & 0 & 23  & 8 & \textbf{39} & 8 & 9 & 6 & 480 & 28 & 61 & \textbf{569} & 76 & 60 & 16 & \textbf{608} & 83 & 68 & 19 \\
		\hline
	\end{tabular} 
\end{table*}

@@

With our 4 settings, we decided to investigate only 2 settings, Simian$_{df}$, and NiCad$_{df}$, and drop Simian$_{\mathrm{\textit{EvaClone}}}$ and NiCad$_{\mathrm{\textit{EvaClone}}}$ due to their large number of false positives as shown in Table \ref{tab:good_classification} and \ref{tab:ok_classification}. With the 2 selected settings, we investigated clone pairs having the minimum clone size of 10 SLOC as they are meaningful and tend to be real clone in modern clone detection \cite{Sajnani2016}.

@@

In this study, we are interested in the effects of online code clones to software development. From the manual investigation of 184 true online clone pairs, we found that there are two potential issues: stale online code, and software licensing violation.
